
\let\nofiles\relax
\documentclass[margin,line]{res}
\usepackage[utf8]{inputenc}
\usepackage{newunicodechar}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{url}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

\newunicodechar{￥}{\textyen}
\DeclareTextCommandDefault{\textyen}{%
  \vphantom{Y}%
  {\ooalign{Y\cr\hidewidth\yenbars\hidewidth\cr}}%
}
\newcommand{\yenbars}{%
  \vbox{
     \hrule height.1ex width.4em
     \kern.15ex
     \hrule height.1ex width.4em
     \kern.3ex
  }%
}


% if using pdflatex:
\setlength{\pdfpagewidth}{\paperwidth}
\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}
\newenvironment{list3}{
	\vspace{-0.13in}
  \begin{list}{}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{-0.0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{-0.0in} \setlength{\partopsep}{-0.0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\renewcommand{\headrulewidth}{0pt}

\begin{document}

\pagestyle{fancy}
\cfoot{}
\rfoot{Page \thepage \ of \pageref{LastPage}}
\name{Mengye Ren \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2in}p{4in}}
10 Kings College Rd, Rm 3302 & {\it Tel:}  +1 (647) 831-6099 \\            
Toronto, Ontario      & {\it Email:}  \url{mren@cs.toronto.edu}\\
Canada, M5S 3G4       & {\it Website:} \url{http://www.cs.toronto.edu/~mren} \\     
\end{tabular}

\section{\sc Research Interests}
Deep learning, computer vision, few-shot learning, continual learning, visual understanding, and biologically plausible deep learning.

\section{\sc Education}
{\bf University of Toronto}\\
{\em Department of Computer Science} \hfill{January 2017 - present}\\
\vspace*{-.1in}
\begin{list1}
\item[] PhD Student, Advisor: Richard S. Zemel
\end{list1}
{\em Department of Computer Science} \hfill{September 2015 - January 2017}\\
\vspace*{-.1in}
\begin{list1}
\item[] MSc, Advisor: Richard S. Zemel
\end{list1}
{\em Department of Engineering Science, ECE Option} \hfill {September 2011 - June 2015}\\
\vspace*{-.1in}
\begin{list1}
\item[] BASc, CGPA 3.90/4.00
\end{list1}

\section{\sc Publications}
The Reversible Residual Network: Backpropagation without Storing Actications. Aidan N. Gomez*, 
\textbf{Mengye Ren}*, Raquel Urtasun, Roger B. Grosse. In \textit{Advances in Neural Information 
Processing Systems (NIPS)}, 2017 (*=equal contribution).

End-to-End Instance Segmentation with Recurrent Attention. 
\textbf{Mengye Ren}, Richard S. Zemel. 
In \textit{Proceedings of IEEE Computer Vision and Pattern Recognition (CVPR)} 2017 (\textbf{spotlight}).

Normalizing the Normalizers: Comparing and Extending Network Normalization 
Schemes. \textbf{Mengye Ren}*, Renjie Liao*, Raquel Urtasun, Fabian H. Sinz, 
Richard S. Zemel. 
In \textit{Proceedings of 5th International Conference on Learning Representations (ICLR)} 2017 (*=equal contribution).

Exploring Models and Data for Image Question Answering. \textbf{Mengye Ren},
Ryan Kiros, Richard Zemel. In \textit{Advances in Neural Information 
Processing Systems (NIPS)}, 2015.

\section{\sc In Preparation}
Meta-Learning for Semi-Supervised Few-Shot Classification. \textbf{Mengye Ren}, Eleni Triantafillou*, 
Sachin Ravi*, Jake Snell, Kevin Swersky, Josh B. Tenenbaum, Hugo Larochelle, Richard S. Zemel.
\textit{NIPS Workshop on Learning with Limited Labeled Data (LLD)}, 2017. (*=equal contribution)

Understanding Short-Horizon Bias in Meta Optimization. Yuhuai Wu*, \textbf{Mengye Ren*}, Renjie Liao,
Roger B. Grosse. 2017 (*=equal contribution).

\section{\sc Teaching}
{\bf University of Toronto}\\
{\em Teaching Assistant} \\%\hfill {January, 2015 - present}\\
\begin{list3}
\item ECE521: Inference Algorithms, Winter 2017.
\item CSC401: Natural Language Computing, Winter 2016.
\item CSC411: Introduction to Machine Learning, Fall 2015, 2016.
\item CSC190: Algorithm and Data Structure, Winter 2015.
\end{list3}

\section{\sc Working Experience}
\begin{tabular*}{\textwidth}{lll@{\extracolsep{\fill}}r}
% \setlength\extrarowheight{5pt}
{\bf Uber ATG} & Toronto, ON & \em{Part-time Engineer II} & May 2017 - Present\\
\multicolumn{3}{l}{Working on research related to faster inference in deep neural networks.}\\
\\[0.0em]
{\bf Twitter} & Cambridge, MA & \em{SWE Intern} & Summer 2016 \\
\multicolumn{3}{l}{Worked on research related to visual relationship discovery.}\\
\\[0.0em]
{\bf Google Brain} & Mountain View, CA & \em{SWE Intern} & Summer 2015\\
\multicolumn{3}{l}{Worked on research related to visual question answering.}\\
\\[0.0em]
{\bf Google} & Mountain View, CA & \em{SWE Intern} & Summer 2014\\
\multicolumn{3}{l}{Worked on a back-end panorama caching system for StreetView.}\\
\\[0.0em]
{\bf Microsoft} & Redmond, WA & \em{SDET Intern} & Summer 2013, 2012\\
\multicolumn{3}{l}{Worked on a code search engine and visualization for Windows app store analytics.}\\
\\[0.0em]
\end{tabular*}

\section{\sc Honors and Awards}
\begin{list2}
\item NIPS 2017 Travel Support, \$800 USD.
\item ICLR 2017 Toulon Travel Award \$1,250 USD.
\item MLSS 2015 Kyoto Travel Support \textyen 140,000 JPY.
\item U of T Quantathon 2nd Place, \$5,000 CAD (with M. Li, J. Nijjer), 2015
\item U of T Undergraduate Mathematics Competition, Honourable Mention, 2015
\item Wallberg Undergraduate Scholarship, \$1,500 CAD, 2014
\item International 5th place in Windward AI Challenge, 1st in U of T (with L. Guo), 2014
\item Dean's List for all semesters, 2011-2015
\item Entrance Scholarship from the University of Toronto, \$5,000 CAD, 2011
\item Meritorious Award in Mathematical Contest of Modeling (MCM), 2011
\end{list2}

\section{\sc Professional Services}
\begin{list2}
\item Conference Reviewer: NIPS 2016/2017, ICML 2017, AAAI 2018, ICLR 2018, CVPR 2018.
\end{list2}

\section{\sc Open Source Softwares}
\begin{list2}
\item TensorFlow Forward-Mode AutoDiff. Forward-mode automatic differentiation for TensorFlow. \\
GitHub: \url{https://github.com/renmengye/tensorflow-forward-ad}
\item DeepDashboard: Real-time web-based training visualizer.\\
GitHub: \url{https://github.com/renmengye/deep-dashboard}
\end{list2}

\section{\sc Invited Talks}
\begin{list2}
\item Sequence-to-Sequence Deep Learning with Recurrent Attention. Queen's University, Kingston, Ontario, Canada. May 2017.
\item Deep Dashboard Tutorial. University of Guelph, Guelph, Ontario, Canada. March 2016.
\item Deep Dashboard Tutorial. University of Toronto, Toronto, Ontario, Canada. Feburary 2016. 
\item Exploring Data and Models for Image Question Answering. ICML 2015 Deep Learning Workshop, Lille, France. July 2015.
\end{list2}

\section{\sc Mentorship}
\begin{list2}
\item Yen-chen Lin, National Tsing Hua University, Intern at Uber ATG, October 2017 - Present.
\item Xinkai Wei, University of Waterloo, Intern at Uber ATG, September 2017 - Present.
\item Yatu Zhang, University of Toronto, Undergraduate Thesis Project, September 2016 - May 2017.
\end{list2}

\end{resume}
\end{document}